Optimal (Multiway) Spatial Joins

### 2024-06-01 5.3.tex
5.3

\noindent \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple in $\J(R_1,...,R_{k-3},H',V)$ satisfying $\cross_{R_{k-2}}(\bm{t}) = \cross_{R_{k-2}}(h^*)$. We can then derive that 
\myeqn{
    \sum_{h^* \in H^*} |\cross_{R_{k-2}}(h^*)| \le \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\cross_{R_{k-2}}(\bm{t})| \leq \out, \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

\noindent To prove the above, we must explain why $r$ contains the effective horizontal segment of $\bm{t}$. Since $r \in \contained_{R_{k-2}}(h^*)$, $r$ covers the segment $[x_1, \minleft(h')] \times y$. Therefore, $[x_1, \minleft(h')] \subseteq [\xleft(r), \xright(r)]$ and $y \in [\ybot(r), \ytop(r)]$.
As $\xright(r)$ is no less than the x-coordinate of $\bm{t}[k-1]$, which we denote as $x$, $[x_1, x] \subseteq [\xleft(r), \xright(r)]$. This implies that $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$, is contained in $r$.

>>>>

\noindent \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\cross_{R_{k-2}}(\bm{t}) = \cross_{R_{k-2}}(h^*)$. We can then derive that 
\myeqn{
    \sum_{h^* \in H^*} |\cross_{R_{k-2}}(h^*)| \le \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\cross_{R_{k-2}}(\bm{t})| \leq \out, \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

\noindent To prove the above, we must explain why $r$ contains the effective horizontal segment of $\bm{t}$. Since $r \in \contained_{R_{k-2}}(h^*)$, $r$ covers the segment $[x_1, \minleft(h')] \times y$. Therefore, $[x_1, \minleft(h')] \subseteq [\xleft(r), \xright(r)]$ and $y \in [\ybot(r), \ytop(r)]$.
As $\xright(r)$ is no less than the x-coordinate of $\bm{t}[k-1]$, which is denoted as $x$, we have $[x_1, x] \subseteq [\xleft(r), \xright(r)]$. This implies that $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$, is contained in $r$.
